Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-03-30 papers/Papers1234/bs-bw-dw-03.tex
Finish intro for Paper III

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Arthur]{
  William J. Henney \& S. J. Arthur\\
  \AddressCRyA
}

@@

In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
presented a taxonomy of stellar bows, which we divided into
wind-supported bow shocks (WBS) and various classes of
radiation-supported bows.  When the dust and gas remains well-coupled
(Paper~I), these are optically thin radiation-supported bow waves
(RBW) and optically thick radiation-supported bow shocks (RBS).  When
the dust decouples from the gas (Paper~II), one has inertia-confined
dust waves (IDW) and drag-confined dust waves (DDW).

>>>>

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Arthur]{
  William J. Henney\thanks{w.henney@irya.unam.mx}
  \& S. J. Arthur\\
  \AddressCRyA
}

@@

Bow-shaped circumstellar nebulae are observed around a wide variety of
stars \citep{Gull:1979a, Cox:2012a, Cordes:1993a} but are most
numerous around luminous OB stars \citep{Kobulnicky:2016a}.  They are
most commonly interpreted as bow shocks, due to a supersonic relative
motion of the surrounding medium, which interacts with the stellar
wind \citep{Wilkin:1996a}.  Early surveys for bow shocks around OB
stars \citep{van-Buren:1995a} concentrated on runaway stars
\citep{Blaauw:1961a, Hoogerwerf:2001a} that have been ejected at high
velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
star clusters or due to the core-collapse supernova explosion of a
binary companion.  However, only a small fraction of runaways show
detectable bow shocks \citep{Huthoff:2002a, Peri:2012a, Peri:2015a,
  Prisegen:2019a}. Targeted searches at mid-infrared wavelengths of
particular high-mass star forming regions such as M17 and RCW~49
\citep{Povich:2008a}, Cygnus~X \citep{Kobulnicky:2010a}, and Carina
\citep{Sexton:2015b} have revealed many bows around slower moving
stars.  In many cases, it may be streaming motions in the interstellar
medium that provide most of the relative velocity: weather vanes
rather than runaways \citep{Povich:2008a}.  More recently, large-scale
surveys of the Galactic Plane \citep{Kobulnicky:2016a,
  Kobulnicky:2017a} and of nearby stars in the Bright Star Catalog
\citep{Bodensteiner:2018a} have revealed hundreds more such bow shocks.

Analytic and semi-analytic thin-shell models of bow shocks have been
developed \citep{van-Buren:1992a, Wilkin:1996a, Canto:1996},
including the effects of non-spherical winds and nonaxisymmetric bows
\citep{Wilkin:2000a, Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.
Increasingly realistic numerical hydrodynamic simulations have been
performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a,
  Meyer:2014b, Mackey:2015a}, including magnetic fields
\citep{Meyer:2017a, Katushkina:2017a, Katushkina:2018a} and detailed
predictions of the dust emission \citep{Meyer:2016a, Acreman:2016a,
  Mackey:2016a}.

% Despite the almost
% universal use of the term ``bow shock'' to describe these objects, it
% may be that slow subsonic velocities of a star through its \hii{}
% region are sufficient \citep{Mackey:2015a, Mackey:2016a} to distort
% the inner stellar wind shock and produce a bow appearance to the
% mid-infrared emission, even though there is no shock in the dusty
% ambient stream.

In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
presented a taxonomy of stellar bows, which we divided into
wind-supported bow shocks (WBS) and various classes of
radiation-supported bows.  When the dust and gas remains well-coupled
(Paper~I), these are optically thin radiation-supported bow waves
(RBW) and optically thick radiation-supported bow shocks (RBS).  When
the dust decouples from the gas (Paper~II), inertia-confined dust
waves (IDW) and drag-confined dust waves (DDW) can result.
